TensorAlloy: an automatic atomistic neural network program for alloys

### 2019-08-26 doc/papers/nn/manuscript.tex
The manuscript is slightly updated.

Figure \ref{fig:benchmark_qm7}a compares the training speed (number of processed 
structures per second) with different batch sizes (number of structures per 
step). It shows that CPU perfers fewer descriptors (radial only) and smallber 
batch size while GPU is suitable for larger batch size and more complicated 
descriptors (radial + angular). 
Figure \ref{fig:benchmark_qm7}b shows the curves of mean absolute errors 
(MAEs, meV/atom) on the test set. This figure clearly illustrate another benefit 
of using larger batch size: the trainings can be much faster. For the best case 
(batch size 100, angular symmetry functions included), the test MAE will reach 5 
meV/atom (1.5 kcal/mol per structure) in just one GPU hour.

@@

\begin{table}[h]
\centering
\begin{tabular}{ccc|cc|c}
\hline
  & \multicolumn{2}{c|}{Energy (meV/atom)} & \multicolumn{2}{c|}{Force (eV/\AA)}
  & Stress (GPa) \\
\hline
Elementary Model & Mo & Ni & Mo & Ni & Mo \\
\hline
Mo & 4.9 (13.2) & & 0.19 (0.25) & & 0.24 (0.87) \\
Ni & & 1.2 (1.2) & & 0.04 (0.05) & \\
\hline
\end{tabular}
\caption{\label{table:MAE1}
Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
stress (GPa) relative to DFT for the two elementary models (Ni, Mo) and their
corresponding SNAP benchmarks (bracket)}
\end{table}

>>>>

Figure \ref{fig:benchmark_qm7}a compares the training speed (number of processed 
structures per second) with different batch sizes (number of structures per 
step). It shows that CPU perfers fewer descriptors (radial only) and smallber 
batch size while GPU is suitable for larger batch size and more complicated 
descriptors (radial + angular). 
Figure \ref{fig:benchmark_qm7}b shows the curves of mean absolute errors 
(MAEs, meV/atom) on the test set. This figure clearly illustrate another benefit 
of using larger batch size: the trainings can be much faster. For the best case 
(batch size 100, angular symmetry functions included), the test MAE will reach 6 
meV/atom (1.8 kcal/mol per structure) in just one GPU hour on our workstation.

@@

\begin{table}[h]
\centering
\begin{tabular}{ccc|cc|c}
\hline
  & \multicolumn{2}{c|}{Energy (meV/atom)} & \multicolumn{2}{c|}{Force (eV/\AA)}
  & Stress (GPa) \\
\hline
Elementary Model & Mo & Ni & Mo & Ni & Mo \\
\hline
Mo & 4.5 (13.2) & & 0.19 (0.25) & & 0.28 (0.87) \\
Ni & & 1.3 (1.2) & & 0.04 (0.05) & \\
\hline
\end{tabular}
\caption{\label{table:MAE1}
Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
stress (GPa) relative to DFT for the two elementary models (Ni, Mo) and their
corresponding SNAP benchmarks (bracket)}
\end{table}
